Solar jet observed at the limb in SDO/SST

### 2016-08-10 paper/ms_temp_paper.tex
Discussion

# # read in some datas
# ha_files = glob('/storage2/jet/SST/*.npy')
# ha_files.sort()
# dop_files = glob('/storage2/jet/dop_arrs/*.npy')
# dop_files.sort()

@@

\begin{pycode}[Temp difference]
import numpy as np
import matplotlib.pyplot as plt
from matplotlib.collections import LineCollection
from matplotlib import colors

@@

From the observation of this feature, we can draw the following conclusions
\begin{itemize}
	\item{This particular feature is visible in H$\alpha$ and He II $30.4$, and thus, is inherently a chromospheric object.}
	\item{The jet has two separate ejections of material.}
	\item{The formation of the jet is observed to be similar to the standard jet formation mechanism.}
	\item{The jet has a rotational component to its motion}
\end{itemize}

The feature is observed to extend to $12.6$ Mm in He II $30.4$ nm (and is only found to be shorter in H$\alpha$ due to moving out of the viewing field of view).
Its lifetime is measured of to be $20$ mins and radial velocities are found to be
This very much puts this feature in the ca

>>>>

@@

\begin{pycode}[jet_temp]
import numpy as np
import matplotlib.pyplot as plt
from matplotlib.collections import LineCollection
from matplotlib import colors

@@

From the observation of this feature, we can draw the following conclusions
\begin{itemize}
	\item{This particular feature is visible in H$\alpha$ and He II $30.4$, and thus, is inherently a chromospheric object.}
	\item{The jet has two separate ejections of material. Reaching a maximum \emph{length} of $25$ Mm}
	\item{The formation of the jet is observed to be similar to the standard jet formation mechanism.}
	\item{The jet has a rotational component to its motion}
\end{itemize}

The feature is observed to extend to $12.6$ Mm in He II $30.4$ nm (and is only found to be shorter in H$\alpha$ due to moving out of the viewing field of view).
Its lifetime is measured of to be $20$ mins and radial velocities are found to be maximised during the initial acceleration, and are of the order $50 - 60$ km$s^{-1}$ during the first acceleration of the feature.
However the second acceleration of material proves awkward to measure accurately, however we estimate slightly higher maximum velocities, but similar averages over the extension upwards. 
This very much puts this feature in the category of macrospicules, agreeing with the recent study by \cite{Bennett2015}.

However the feature exhibits similar formation mechanisms as a standard jet following the pattern demonstrated in \cite{Shibata1992} and then built on by \cite{Moore2010}, who also presented the blowout jet mechanism.
With the two visible bright points in the H$\alpha$ images which come to form an, all be it, long thin bright arch before forming the characteristic spire of a the standard jet.
Unfortunatley, Hinode's XRT instrument was in a power down mode during the formation of this feature and RHESSI did not record the event, as such, we are missing crucial X-ray data.

If an increase in the X-ray radiation were to be found, the question as to the categorisation of such a feature becomes important.
Given that we observe several of the key indicators of a standard jet, could this not also be classified as a standard jet? 
Inspite of this features relatively small size, this could be classified as an X-ray jet.
However the question remains, is this a macrospicule?
And if so, do we classify the feature as a macrospicule or a standard jet?

One possible differentiator is the appearance in the higher coronal wavelengths.
In this case, the jet appears as an absorption feature, against the brighter limb.
This does not mean that the jet does not reach coronal temperatures, in $30.4$ nm the jet appears as absorption below the limb and as emission above it.
We cannot conclusively say that the jet contributes to the coronal emission by visual inspection.

Therefore, we propose that this is a standard jet, and as a community, we need to fully address the underlying physics of macrospicules.
This is despite the ambiguity about its appearance in the coronal emission lines, but the underlying physics is enough to draw this conclusion.
